full title

### 2020-11-21 paper/pldi21/javascript.tex
Updated javascript.tex

We define the symbolic states with the extended concrete values and the abstract
counters for addresses as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
(\absimapset \times \symbstset)$ from pairs of views and abstract states to the
corresponding pairs of abstract instantiation maps and sealed symbolic states.
The algorithm is to traverse the averall structure, to remain a single value,
but changes to each abstract value represents multiple values to a new symbol
and adds the mapping from the new symbol to the original abstract value.  In a
reverse way, the opposite converter $\saconverter: (\absimapset \times
\symbstset)  \rightarrow (\viewset \times \absdom)$ recovers the abstract values
based on the given abstract instantiation map.  The symbolic transition relation
$\symbtrans$ is an extension of the original concrete transition relation
$\trans$.  When the exact values of symbolic values are required, symbolic
states have the symbolic transition relation with the exception state $\excst$.
For example, we add the following rule for $\kwret$ statements:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\st}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \st = (\lab, \mem, \ctxt, \addr)
    \trans \excst
  }
\end{mathpar}
We extend each rule of concrete semantics to support such behaviors of symbolic
values.

>>>>

We define the sealed symbolic states by not only extending the concrete values
$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
The objects in JavaScript are open thus their properties can be dynamically
added or deleted.  Moreover, the object properties are accessible via string
values thus it is difficult to decide whether the strong udpates are possible or
not in static analysis.  To check the possibility of strong updates during
sealed symbolic execution, we augmented its states with the abstract counters
$\abscountset$.  Then, we define the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$ by traversing the averall
structure of given abstract states to keep singleton values but to change each
abstract value to a unique symbolic value.  During the traverse, we also keep
the mapping from symbolic values to the corresponding abstract values to
construct an abstract instantiation map.  For the opposite converter
$\saconverter: (\absimapset \times \symbstset)  \rightarrow (\viewset \times
\absdom)$, we just recovers the abstract values using the given abstract
instantiation map.  We only define the sealed symbolic transition relation
$\symbtrans$ when the next step does not require actual values of any symbolic
values.  If not, a given sealed symbolic state does not have sealed symbolic
transitions with any other ones.  For example, we add the following rule for
$\kwret$ statements:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\st}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \st = (\lab, \mem, \ctxt, \addr)
    \trans \excst
  }
\end{mathpar}
We extend each rule of concrete semantics to support such behaviors of symbolic
values.
